---
title: "PopulationComparisonsCA"
output: html_document
date: "2023-08-15"
---


0. Load packages and data
1. Fill and create necessary columns for each population
2. Select relevant columns
3. Create output datasheet
4. Creating larval survival graphs (should be moved to new datasheet)
5. Random analyses
6. Creating a pupal combined datasheet



#0. Load packages and data

```{r}
library(dplyr)
library(lubridate)
library(Rmisc)
library(ggplot2)
```

## Larval Data
```{r}
NC1 <- read.csv("~/Desktop/GitHub/Pieris/North_Carolina/NC_Larval_and_Realistic_Temps/Data/CleanedRound1.csv", header = T)
NC2 <- read.csv("~/Desktop/GitHub/Pieris/NCLarval2023.csv", header= T)
WA1 <- read.csv("~/Desktop/GitHub/Pieris/Washington/DataWA/CleanedBlock1.csv", header = T)
WA1wide <- read.csv("~/Desktop/GitHub/Pieris/Washington/DataWA/WABlock1Dev.csv", header = T)
WA2 <- read.csv("~/Desktop/GitHub/Pieris/Washington/DataWA/CleanedBlock2.csv", header = T)
WA2wide <- read.csv("~/Desktop/GitHub/Pieris/Washington/DataWA/WABlock2Dev.csv", header = T)
CA <- read.csv("~/Desktop/GitHub/Pieris/California/CALarval/CAPierisLarvalData.csv", header = T)
```

#1. Fill and create necessary columns for each population
## Converting Mass.adult column from character to numeric
``` {r}
CA$Mass.adult <- as.numeric(CA$Mass.adult)

```

 Fill unfilled columns at survival for each stage

## Surv.4th
```{r}
for (i in 1:length(CA$Surv.4th)){
  if(is.na(CA[i,7])== TRUE){
    CA[i,5] <- "N"
  } else if(is.na(CA[i,7])== FALSE){
    CA[i,5] <- "Y"
  }
}
```

## Surv.5th
```{r}
for (i in 1:length(CA$Surv.5th)){
  if(is.na(CA[i,11])== TRUE){
    CA[i,9] <- "N"
  } else if(is.na(CA[i,11])== FALSE){
    CA[i,9] <- "Y"
  }
}
```

## Surv.pupa
```{r}
for (i in 1:length(CA$Surv.pupa)){
  if(is.na(CA[i,15])== TRUE){
    CA[i,13] <- "N"
  } else if(is.na(CA[i,15])== FALSE){
    CA[i,13] <- "Y"
  }
}
```

## Surv.adult
```{r}
for (i in 1:length(CA$Surv.adult)){
  if(is.na(CA[i,20])== TRUE){
    CA[i,18] <- "N"
  } else if(is.na(CA[i,20])== FALSE){
    CA[i,18] <- "Y"
  }
}
```

first I need to make sure that all intermediates are labeled as dead on the day they failed to pupate
```{r}
for (i in 1:length(CA$Date.dead)) {
  if  (CA[i, 17] == "no"){
    CA[i, 24] = CA[i,15]}
}
```

Next lets add the prepupual death column

```{r}
CA$Time.prepupal.death <- NA
```

```{r}
for(i in 1:length(CA$Time.prepupal.death)) { 
  if (CA[i, 17] == "yes"){
    CA[i, 27] <- NA
  } else if (CA[i, 17] != "yes"){
    CA[i, 27] <- CA[i, 25]
  }
}
```


Also, lets change all "yes" and "no" to "Y" and "N" for consistency 

```{r}
CA <- data.frame(lapply(CA, function(x) {
          gsub("no", "N", x)
}))

CA <- data.frame(lapply(CA, function(x) {
          gsub("yes", "Y", x)
}))

```



NC pop round 1

```{r}
NC1$Time.prepupal.death <- NA
```

```{r}
for(i in 1:length(NC1$Time.prepupal.death)) { 
  if (NC1[i, 19] == "Y"){
    NC1[i, 30] <- NA
  } else if (NC1[i, 19] != "Y"){
    NC1[i, 30] <- NC1[i, 27]
  }
}
```

NC pop round 2

Fill unfilled columns at survival for each stage

## Surv.4th
```{r}
for (i in 1:length(NC2$Surv.4th)){
  if(is.na(NC2[i,9])== TRUE){
    NC2[i,7] <- "N"
  } else if(is.na(NC2[i,9])== FALSE){
    NC2[i,7] <- "Y"
  }
}
```

## Surv.5th
```{r}
for (i in 1:length(NC2$Surv.5th)){
  if(is.na(NC2[i,13])== TRUE){
    NC2[i,11] <- "N"
  } else if(is.na(NC2[i,13])== FALSE){
    NC2[i,11] <- "Y"
  }
}
```

## Surv.pupa
```{r}
for (i in 1:length(NC2$Surv.pupa)){
  if(is.na(NC2[i,17])== TRUE){
    NC2[i,15] <- "N"
  } else if(is.na(NC2[i,17])== FALSE){
    NC2[i,15] <- "Y"
  }
}
```

## Surv.eclose
```{r}
for (i in 1:length(NC2$Surv.eclose)){
  if(is.na(NC2[i,22])== TRUE){
    NC2[i,20] <- "N"
  } else if(is.na(NC2[i,22])== FALSE){
    NC2[i,20] <- "Y"
  }
}
```

first I need to make sure that all intermediates are labeled as dead on the day they failed to pupate
```{r}
for (i in 1:length(NC2$Date.dead)) {
  if  (NC2[i, 19] == "N"){
    NC2[i, 26] = NC2[i,16]}
}
```

Next lets add the prepupual death column

```{r}
NC2$Time.prepupal.death <- NA
```

```{r}
for(i in 1:length(NC2$Time.prepupal.death)) { 
  if (NC2[i, 19] == "Y"){
    NC2[i, 29] <- NA
  } else if (NC2[i, 19] != "yes"){
    NC2[i, 29] <- NC2[i, 27]
  }
}
```




Washington pops:


```{r}
# Internal process of the loop to convert days to dates
expt_day <- function(start.date, date){
  date <- mdy(date)
  start <- mdy(start.date)
  diff <- yday(date) - yday(start)

  return(diff)
}

# Code for the loop itself
loop <- function(start.date, date.list){
  days <- rep(NA, length(date.list))
  for (i in 1:(length(days))){
    days[i] <- expt_day(start.date = start.date, date = date.list[i])
  }
  return(days)
}
```


We need to combine all of these different "death" conditions and select only the ones that died prior to pupation. Let's write a giant for loop, so that we don't have to do it by hand in Excel. 

```{r}
WA1wide$Prepupal.death <- NA

WA1wide[22, 15] <- 150
```


```{r}
for (i in 1:length(WA1wide$Prepupal.death)){
  if (is.na(WA1wide[i, 15]) == FALSE){
    WA1wide[i, 26] <- NA
  } else if (is.na(WA1wide[i, 15]) == TRUE){
    if (is.na(WA1wide[i, 17]) == FALSE) {
      WA1wide[i, 26] <- WA1wide[i, 16]
    } else if (is.na(WA1wide[i, 17]) == TRUE) {
      WA1wide[i, 26] <- WA1wide[i, 21]
    }
  
  }
  
}  
```




```{r}
WA1wide$day.hatch <- loop(start.date = "11/16/2022", date.list = WA1wide$Date.hatch)
WA1wide$Prepupal.death.day <- loop(start.date = "11/16/2022", date.list = WA1wide$Prepupal.death)
```

**Above code is busted if it crosses the year mark. Gotta add 365 to the negative numbers**

```{r}
for (i in 1:length(WA1wide$Prepupal.death.day)){
  if (is.na(WA1wide[i, 28]) == FALSE){
      if (WA1wide[i, 28] < 0) {
      WA1wide[i, 28] <- WA1wide[i, 28] + 365
    } else if (WA1wide[i, 28] >= 0) {
     WA1wide[i, 28] <- WA1wide[i, 28]
    }
  } else if (is.na(WA1wide[i, 28]) == TRUE){
    WA1wide[i, 28] <- NA
  }

}
```



```{r}
WA1wide$Age.prepupal.death <- WA1wide$Prepupal.death.day - WA1wide$day.hatch
```

**REPEAT FOR WA2**

```{r}
WA2wide$Prepupal.death <- NA

WA2wide[55, 14] <- 150
```


```{r}
for (i in 1:length(WA2wide$Prepupal.death)){
  if (is.na(WA2wide[i, 14]) == FALSE){
    WA2wide[i, 25] <- NA
  } else if (is.na(WA2wide[i, 14]) == TRUE){
    if (is.na(WA2wide[i, 16]) == FALSE) {
      WA2wide[i, 25] <- WA2wide[i, 15]
    } else if (is.na(WA2wide[i, 16]) == TRUE) {
      WA2wide[i, 25] <- WA2wide[i, 20]
    }
  
  }
  
}  
```


```{r}
WA2wide$day.hatch <- loop(start.date = "11/30/2022", date.list = WA2wide$Date.hatch)
WA2wide$Prepupal.death.day <- loop(start.date = "11/30/2022", date.list = WA2wide$Prepupal.death)
```

**Above code is busted if it crosses the year mark. Gotta add 365 to the negative numbers**

```{r}
for (i in 1:length(WA2wide$Prepupal.death.day)){
  if (is.na(WA2wide[i, 27]) == FALSE){
      if (WA2wide[i, 27] < 0) {
      WA2wide[i, 27] <- WA2wide[i, 27] + 365
    } else if (WA2wide[i, 27] >= 0) {
     WA2wide[i, 27] <- WA2wide[i, 27]
    }
  } else if (is.na(WA2wide[i, 27]) == TRUE){
    WA2wide[i, 27] <- NA
  }

}
```


```{r}
WA2wide$Age.prepupal.death <- WA2wide$Prepupal.death.day - WA2wide$day.hatch
```

#2. Select the relevant columns


```{r}
CASum <- CA %>%
  select(CID = CID, Treatment = Mean.temp, Age.death = Time.prepupal.death, Surv.pupa, PupateOK = Pupate.ok, 
         Age.pupa = Time.pupa, Mass.pupa = Mass.pupa)

CASum$Expt <- "CA"
CASum$Population <- "CA"
```


```{r}
NC1Sum <- NC1 %>%
  select(CID = CID, Treatment = Mean.Temp, Age.death = Time.prepupal.death, Surv.pupa, PupateOK = PupateOk, 
         Age.pupa = Time.pupa, Mass.pupa = Mass.pupa)

NC1Sum$Expt <- "NC1"
NC1Sum$Population <- "NC"
```


```{r}
NC2Sum <- NC2 %>%
  select(CID = CID, Treatment = Mean.temp, Age.death = Time.prepupal.death, Surv.pupa, PupateOK = Pupate.ok, 
         Age.pupa = Time.pupa, Mass.pupa = Mass.pupa)

NC2Sum$Expt <- "NC2"
NC2Sum$Population <- "NC"
```

```{r}
WA1wide <- WA1wide %>%
  select(CID = CID, Treatment = Treatment, Age.death = Age.prepupal.death, Mass.pupa = Mass.pupa)

WA1Sum <- WA1 %>%
  select(CID = CID, Treatment = Treatment, Surv.pupa, PupateOK, Age.pupa = DaysHtoP)

WA1merge <- merge(WA1wide, WA1Sum, by = c("CID", "Treatment"))

WA1merge$Expt <- "WA1"
WA1merge$Population <- "WA"
```


```{r}
WA2wide <- WA2wide %>%
  select(CID = CID, Treatment = Treatment, Age.death = Age.prepupal.death, Mass.pupa = Mass.pupa)

WA2Sum <- WA2 %>%
  select(CID = CID, Treatment = Treatment, Surv.pupa, PupateOK, Age.pupa = DaysHtoP)

WA2merge <- merge(WA2wide, WA2Sum, by = c("CID", "Treatment"))

WA2merge$Expt <- "WA2"
WA2merge$Population <- "WA"
```

#3. Combine and output

```{r}
output <- rbind(NC1Sum, NC2Sum)

output <-rbind(output, WA1merge)

output <- rbind(output, WA2merge)

output <- rbind(output, CASum)

```


```{r}
write.csv(output, file = "~/Desktop/GitHub/Pieris/PopulationCombData.csv")
```


#4. Survival Analysis

##4a. NC1 
```{r}
NC1SurvSum <- summarySE(data = NC1, 
                         measurevar = "Mass.pupa", 
                         groupvars = c("Mean.Temp", "Surv.pupa"))
NC1SurvSum
```

```{r}
NC1SurvData <- data.frame(Mean.Temp = c(16, 21, 26, 30, 34), 
                       surv.perc = 0, 
                       Population = "NC",
                       Group = "NC1")

NC1SurvData$Mean.Temp <- as.factor(NC1SurvData$Mean.Temp)
NC1SurvData$Group = as.factor(NC1SurvData$Group)
```

```{r}
NC1SurvData[1, 2] <- NC1SurvSum[2, 3] / (NC1SurvSum[2, 3] + NC1SurvSum[1, 3])
NC1SurvData[2, 2] <- NC1SurvSum[4, 3] / (NC1SurvSum[4, 3] + NC1SurvSum[3, 3])
NC1SurvData[3, 2] <- NC1SurvSum[6, 3] / (NC1SurvSum[6, 3] + NC1SurvSum[5, 3])
NC1SurvData[4, 2] <- NC1SurvSum[8, 3] / (NC1SurvSum[8, 3] + NC1SurvSum[7, 3])
NC1SurvData[5, 2] <- NC1SurvSum[10, 3] / (NC1SurvSum[10, 3] + NC1SurvSum[9, 3])
```

##4b. NC2 
```{r}
NC2SurvSum <- summarySE(data = NC2, 
                         measurevar = "Mass.pupa", 
                         groupvars = c("Mean.temp", "Surv.pupa"))
NC2SurvSum
```


```{r}
NC2SurvData <- data.frame(Mean.Temp = c(16, 21, 26, 30, 34), 
                       surv.perc = 0, 
                       Population = "NC",
                       Group = "NC2")

NC2SurvData$Mean.Temp <- as.factor(NC2SurvData$Mean.Temp)
NC2SurvData$Group = as.factor(NC2SurvData$Group)
```


```{r}
NC2SurvData[1, 2] <- NC2SurvSum[2, 3] / (NC2SurvSum[2, 3] + NC2SurvSum[1, 3])
NC2SurvData[2, 2] <- NC2SurvSum[4, 3] / (NC2SurvSum[4, 3] + NC2SurvSum[3, 3])
NC2SurvData[3, 2] <- NA
NC2SurvData[4, 2] <- NA
NC2SurvData[5, 2] <- NC2SurvSum[6, 3] / (NC2SurvSum[6, 3] + NC2SurvSum[5, 3])
```


##4c. WA1
```{r}
WA1SurvSum <- summarySE(data = WA1, 
                         measurevar = "Mass.pupa", 
                         groupvars = c("Treatment", "Surv.pupa"))
WA1SurvSum
```


```{r}
WA1SurvData <- data.frame(Mean.Temp = c(16, 21, 26, 30, 34), 
                       surv.perc = 0, 
                       Population = "WA",
                       Group = "WA1")

WA1SurvData$Mean.Temp <- as.factor(WA1SurvData$Mean.Temp)
WA1SurvData$Group = as.factor(WA1SurvData$Group)
```


```{r}
WA1SurvData[1, 2] <- WA1SurvSum[2, 3] / (WA1SurvSum[2, 3] + WA1SurvSum[1, 3])
WA1SurvData[2, 2] <- WA1SurvSum[4, 3] / (WA1SurvSum[4, 3] + WA1SurvSum[3, 3])
WA1SurvData[3, 2] <- WA1SurvSum[6, 3] / (WA1SurvSum[6, 3] + WA1SurvSum[5, 3])
WA1SurvData[4, 2] <- WA1SurvSum[8, 3] / (WA1SurvSum[8, 3] + WA1SurvSum[7, 3])
WA1SurvData[5, 2] <- WA1SurvSum[10, 3] / (WA1SurvSum[10, 3] + WA1SurvSum[9, 3])
```

##4d. WA2
```{r}
WA2SurvSum <- summarySE(data = WA2, 
                         measurevar = "Mass.pupa", 
                         groupvars = c("Treatment", "Surv.pupa"))
WA2SurvSum
```


```{r}
WA2SurvData <- data.frame(Mean.Temp = c(16, 21, 26, 30, 34), 
                       surv.perc = 0, 
                       Population = "WA",
                       Group = "WA2")

WA2SurvData$Mean.Temp <- as.factor(WA2SurvData$Mean.Temp)
WA2SurvData$Group = as.factor(WA2SurvData$Group)
```


```{r}
WA2SurvData[1, 2] <- WA2SurvSum[2, 3] / (WA2SurvSum[2, 3] + WA2SurvSum[1, 3])
WA2SurvData[2, 2] <- WA2SurvSum[4, 3] / (WA2SurvSum[4, 3] + WA2SurvSum[3, 3])
WA2SurvData[3, 2] <- WA2SurvSum[6, 3] / (WA2SurvSum[6, 3] + WA2SurvSum[5, 3])
WA2SurvData[4, 2] <- WA2SurvSum[8, 3] / (WA2SurvSum[8, 3] + WA2SurvSum[7, 3])
WA2SurvData[5, 2] <- WA2SurvSum[10, 3] / (WA2SurvSum[10, 3] + WA2SurvSum[9, 3])
```


##4e. CA
```{r}
CASurvSum <- summarySE(data = CA, 
                         measurevar = "Mass.pupa", 
                         groupvars = c("Mean.temp", "Surv.pupa"))
CASurvSum
```


```{r}
CASurvData <- data.frame(Mean.Temp = c(16, 21, 26, 30, 34), 
                       surv.perc = 0, 
                       Population = "CA")

CASurvData$Mean.Temp <- as.factor(CASurvData$Mean.Temp)
```


```{r}
CASurvData[1, 2] <- CASurvSum[2, 3] / (CASurvSum[2, 3] + CASurvSum[1, 3])
CASurvData[2, 2] <- CASurvSum[4, 3] / (CASurvSum[4, 3] + CASurvSum[3, 3])
CASurvData[3, 2] <- CASurvSum[6, 3] / (CASurvSum[6, 3] + CASurvSum[5, 3])
CASurvData[4, 2] <- CASurvSum[8, 3] / (CASurvSum[8, 3] + CASurvSum[7, 3])
CASurvData[5, 2] <- CASurvSum[10, 3] / (CASurvSum[10, 3] + CASurvSum[9, 3])
```


##4f. Combine survival data for each population 

```{r}
NCCombSurv <- merge(NC1SurvData, NC2SurvData, by = c("Mean.Temp","Population")) 
NCCombSurv <- NCCombSurv %>% select(Mean.Temp, Population, surv.perc.x, surv.perc.y)
NCCombSurv$surv.perc <- rowMeans(NCCombSurv[3:4], na.rm = TRUE)
NCCombSurv <- NCCombSurv %>% select(Mean.Temp, surv.perc, Population)

WACombSurv <- merge(WA1SurvData, WA2SurvData, by = c("Mean.Temp", "Population"))
WACombSurv <- WACombSurv %>% select(Mean.Temp, Population, surv.perc.x, surv.perc.y)
WACombSurv$surv.perc <- rowMeans(WACombSurv[3:4], na.rm= TRUE)
WACombSurv <- WACombSurv %>% select(Mean.Temp, surv.perc, Population)

combsurv <- rbind(NCCombSurv, WACombSurv)

combsurv <-rbind(combsurv, CASurvData)

```

This doesn't work anymore after data changed
```{r}
combsurvlinegraph <- ggplot(data = combsurv, aes(x = Mean.Temp, y = surv.perc, group = Population, color = Population)) + 
  theme_bw() + 
  geom_point(size = 2) + 
  geom_line() + 
  ylim(0, 1) + 
   scale_color_manual(values = c("purple", "#1E88E5", "orange", "lime green", "#D81B60")) + 
  labs(x = "Mean Rearing Temperature", y = "Proportion survival to pupation")

combsurvlinegraph
```
```{r}
ggsave("~/Desktop/GitHub/Pieris/Survivalplotuncombined.png", combsurvlinegraph, width = 8, height = 5)
```

```{r}
combsurvgraph <- ggplot(data = combsurv, aes(x = Mean.Temp, y = surv.perc, group = Population, color = Population)) + 
  theme_bw() + 
  geom_point(size = 2) + 
  geom_line() + 
  ylim(0, 1) + 
   scale_color_manual(values = c("purple", "#1E88E5", "orange", "lime green", "#D81B60")) + 
  labs(x = "Mean Rearing Temperature", y = "Proportion survival to pupation")

combsurvgraph
```
```{r}
ggsave("~/Desktop/GitHub/Pieris/Survivallineplotcombined.png", combsurvgraph, width = 8, height = 5)
```



```{r}
combsurvbargraph <- ggplot(data = combsurv, aes(x= Mean.Temp, y= surv.perc, fill = Population)) + 
  geom_bar(stat = "identity", position= position_dodge())+ 
  theme_bw() +
  scale_fill_manual(values = c("purple", "#1E88E5", "orange", "lime green", "#D81B60")) + 
  labs(x = "Mean Rearing Temperature", y = "Proportion survival to pupation")

combsurvbargraph
```
```{r}
ggsave("~/Desktop/GitHub/Pieris/Survivalbarcombined.png", combsurvbargraph, width = 8, height = 5)
```


#5. Random Analysis

```{r}
mod1<- lm(Age.pupa ~ Treatment * Population, data= output)

summary(mod1)
anova(mod1)
```




#6. Creating a combined pupal datasheet
```{r}
NCPupal <- read.csv("~/Desktop/GitHub/Pieris/North_Carolina/NC Pupal/Data/NCPupal2023.csv" , header = T)
CAPupal <- read.csv("~/Desktop/GitHub/Pieris/California/CAPupal/CAPupal2023.csv", header = T)
CAPupal26 <- read.csv("~/Desktop/GitHub/Pieris/California/CAPupal/CAPupal26Deg.csv", header = T)
WAPupal <- read.csv("~/Desktop/GitHub/Pieris/Washington/DataWA/WAPupa.csv", header = T)
```

```{r}
WAPupal$Emerge.ok <- NA

for (i in 1:length(WAPupal$Emerge.ok)){
  if(is.na(WAPupal[i,19])== TRUE){
    WAPupal[i,21] <- "No"
  } else if(is.na(WAPupal[i,19])== FALSE){
    WAPupal[i,21] <- "Yes"
  }
}
```


```{r}
WAPupal$Pupate.ok <- NA

for (i in 1:length(WAPupal$Pupate.ok)){
  if(is.na(WAPupal[i,12])== TRUE){
    WAPupal[i,22] <- "Yes"
  } else if(is.na(WAPupal[i,12])== FALSE){
    WAPupal[i,22] <- "No"
  }
}

```

```{r}
WAPupal$Surv.eclose <- NA

for (i in 1:length(WAPupal$Mass.adult)){
  if(is.na(WAPupal[i,16])== TRUE){
    WAPupal[i,23] <- "No"
  } else if(is.na(WAPupal[i,16])== FALSE){
    WAPupal[i,23] <- "Yes"
  }
}
```

```{r}
for (i in 1:length(NCPupal$Mass.adult)){
  if(is.na(NCPupal[i,19])== TRUE){
    NCPupal[i,21] <- "No"
  } else if(is.na(NCPupal[i,19])== FALSE){
    NCPupal[i,21] <- "Yes"
  }
}
```

```{r}
CAPupal$Surv.eclose <- NA

for (i in 1:length(CAPupal$Mass.adult)){
  if(is.na(CAPupal[i,14])== TRUE){
    CAPupal[i,21] <- "No"
  } else if(is.na(CAPupal[i,14])== FALSE){
    CAPupal[i,21] <- "Yes"
  }
}
```

```{r}
CAPupal26$Surv.eclose <- NA

for (i in 1:length(CAPupal26$Mass.adult)){
  if(is.na(CAPupal26[i,21])== TRUE){
    CAPupal26[i,28] <- "No"
  } else if(is.na(CAPupal26[i,21])== FALSE){
    CAPupal26[i,28] <- "Yes"
  }
}
```

```{r}
NCPupal <- NCPupal %>% select(Treatment, DaysHtoP, DaysPtoE, Pupate.ok, Emerge.ok, Mass.adult, Surv.eclose)
NCPupal$Population <- "NC"
CAPupal <- CAPupal %>% select(Treatment, DaysHtoP, DaysPtoE, Pupate.ok, Emerge.ok, Mass.adult, Surv.eclose)
CAPupal$Population <- "CA"
CAPupal26 <- CAPupal26 %>% select(Treatment, DaysHtoP, DaysPtoE, Pupate.ok, Eclose.ok, Mass.adult, Surv.eclose)
CAPupal26$Population <- "CA"
WAPupal <- WAPupal %>% select(Trt, DaysHtoP, DaysPtoE, Pupate.ok, Emerge.ok, Mass.adult, Surv.eclose)
WAPupal$Population <- "WA"
```


```{r}
colnames(WAPupal)[1] = "Treatment"
colnames(CAPupal26)[5] = "Emerge.ok"
```

```{r}
PupalComb <- rbind(NCPupal, CAPupal)
PupalComb <- rbind(PupalComb, CAPupal26)
PupalComb <- rbind(PupalComb, WAPupal)
```


```{r}
write.csv(PupalComb, file = "~/Desktop/GitHub/Pieris/PupalCombData.csv")
```




