---
title: "Round 2 Analysis "
output: html_notebook
---

Let's compare our predictions to the round 2 data. 

# 0. Load in the data and packages

```{r}
library(Rmisc)
library(ggplot2)
library(tidyverse)
```

```{r}
round2 <- read.csv("~/Desktop/GitHub/Pieris/NCLarvalRealTemps2022.csv", header = TRUE)

round2 <- round2[round2$CID != 77, ]
round2 <- round2[round2$CID != 46, ]
```

# 1. Clean the data

## Larval pupal intermediates are considered larval deaths because they aren't considered pupal deaths
```{r}
for (i in 1:length(round2$Surv.pupa)){
  if(is.na(round2[i,17])== TRUE || round2[i,18] == "N" ){
    round2[i,14] <- "No"
  } else if(is.na(round2[i,17])== FALSE){
    round2[i,14] <- "Yes"
  }
}

```

# 2. Get means for pupal mass and development rate

## Pupal mass

Separating out LPI and successful pupae 

### Mean mass and SE

```{r}
pupalmeans2 <- summarySE(data = round2[round2$Surv.pupa == "Y", ], measurevar = "Mass.pupa", groupvars = c("Treatment", "PupateOK"))

pupalmeans2

pupalmeans2$Mass.se <- pupalmeans2$se

pupalmeans2 <- pupalmeans2 %>%
  select(Treatment, PupateOK, N, Mass.pupa, Mass.se)


```

### Mean dev time and SE

```{r}
pupaltimemeans2 <- summarySE(data = round2[round2$Surv.pupa == "Y", ], measurevar = "Time.pupa", groupvars = c("Treatment", "PupateOK"))

pupaltimemeans2

pupaltimemeans2$Time.se <- pupaltimemeans2$se

pupaltimemeans2 <- pupaltimemeans2 %>%
  select(Treatment, PupateOK, N, Time.pupa, Time.se)
```

### Merge together

```{r}
pupalmeans2 <- merge(pupalmeans2, pupaltimemeans2, by = c("Treatment", "PupateOK", "N"))
```


## Add in dvelopment rate

```{r}
round2$Dev.Rate <- 1 / (round2$Time.pupa)
```

```{r}
pupalratemeans2 <- summarySE(data = round2[round2$Surv.pupa == "Y", ], measurevar = "Dev.Rate", groupvars = c("Treatment", "PupateOK"))

pupalratemeans2

pupalratemeans2$Rate.se <- pupalratemeans2$se

pupalratemeans2 <- pupalratemeans2 %>%
  select(Treatment, PupateOK, N, Dev.Rate, Rate.se)
```


```{r}
pupalmeans2 <- merge(pupalmeans2, pupalratemeans2, by = c("Treatment", "PupateOK", "N"))
```


# Get new values with both successful and unsuccessful pupations

Apr prediction: 33.42
Aug prediction: 12.92


```{r}
pupaltimemeans2total <- summarySE(data = round2[round2$Surv.pupa == "Y", ], measurevar = "Time.pupa", groupvars = c("Treatment"))

pupaltimemeans2total

pupaltimemeans2total$Time.se <- pupaltimemeans2total$se

pupaltimemeans2total <- pupaltimemeans2total %>%
  select(Treatment, N, Time.pupa, Time.se)
```


```{r}
pupalratemeans2total <- summarySE(data = round2[round2$Surv.pupa == "Y", ], measurevar = "Dev.Rate", groupvars = c("Treatment"))

pupalratemeans2total

pupalratemeans2total$Rate.se <- pupalratemeans2total$se

pupalratemeans2total <- pupalratemeans2total %>%
  select(Treatment, N, Dev.Rate, Rate.se)
```

#3. Getting survival data to report
```{r}
survpercsum <- summarySE(data = round2, 
                         measurevar = "CID", 
                         groupvars = c("Treatment", "Surv.pupa"))

survpercsum
```

April surv rate is 8/60= .13
August surv rate is 29/61 = .48





