---
title: "Comparing NC WA, and CA data"
output: html_notebook
---
0. load packages and data
1. larval dev rate vs temp
2. pupal mass vs temp
3. surv to pupation vs temp
4. north carolina blocked larval dev rate comparison


# 0. Load packages and data

```{r}
library(dplyr)
library(ggplot2)
library(Rmisc)
```

```{r}
comb <- read.csv("~/Desktop/GitHub/Pieris/PopulationCombData.csv", header = TRUE)
NC2 <- read.csv("~/Desktop/GitHub/Pieris/NCLarval2023.csv", header= T)
```


# 1. larval dev rate vs. temp 
  - Include LPIs 
  
```{r}
comb$Dev.rate <- 1/comb$Age.pupa
```


```{r}
devratemeans <- summarySE(data = comb[comb$Surv.pupa == "Y", ], 
                               measurevar = "Dev.rate", 
                               groupvars = c("Treatment", "Population"))

devratemeans

devratemeans$Treatment <- as.factor(devratemeans$Treatment)
```



```{r}
NCWACAdevrate <- ggplot(data = devratemeans, aes(x = Treatment, y = Dev.rate, group = Population, linetype = Population, 
                                       shape = Population)) + 
  theme_bw() + 
  geom_point(size = 3) + 
  geom_line() +
  labs(x = "Mean Rearing Temperature", y = "Development Rate", group = "Population", linetype = "Population", 
       shape = "Population") +
  scale_linetype_manual(values = c("solid", "dashed", "dotted")) + 
  scale_shape_manual(values = c(19, 2, 5)) + 
  geom_errorbar(aes(ymin = Dev.rate - se, ymax = Dev.rate + se), width = 0.3, linetype = "solid")

NCWACAdevrate
  
```

```{r}
ggsave("~/Desktop/GitHub/Pieris/NCWACAdevrate.png", NCWACAdevrate, width = 8, height = 5)
```



# 2. Pupal mass vs. temp
  - Exclude LPIs
  

```{r}
massmeans <- summarySE(data = comb[comb$Surv.pupa == "Y" & comb$PupateOK == "Y" & !is.na(comb$Mass.pupa), ], 
                               measurevar = "Mass.pupa", 
                               groupvars = c("Treatment", "Population"))

massmeans

massmeans$Treatment <- as.factor(massmeans$Treatment)
```



```{r}
NCWACAmass <- ggplot(data = massmeans, aes(x = Treatment, y = Mass.pupa, group = Population, linetype = Population, 
                                       shape = Population)) + 
  theme_bw() + 
  geom_point(size = 3) + 
  geom_line() +
  labs(x = "Mean Rearing Temperature", y = "Pupal Mass", group = "Population", linetype = "Population", 
       shape = "Population") +
  scale_linetype_manual(values = c("solid", "dashed", "dotted")) + 
  scale_shape_manual(values = c(19, 2, 5)) + 
  geom_errorbar(aes(ymin = Mass.pupa - se, ymax = Mass.pupa + se), width = 0.3, linetype = "solid")

NCWACAmass
  
```


```{r}
ggsave("~/Desktop/GitHub/Pieris/NCWACAmass.png", NCWACAmass, width = 8, height = 5)
```


# 3. Surv to pupation vs. temp
  - Include LPIs
  

```{r}
survpercsum <- summarySE(data = comb, 
                         measurevar = "CID", 
                         groupvars = c("Treatment", "Expt", "Surv.pupa"))

survpercsum
```


```{r}
survdata <- data.frame(Treatment = rep(c(16, 21, 26, 30, 34), times = 4), 
                       surv.perc = 0, 
                       Expt = rep(c("NC", "WA1", "WA2", "CA"), each = 5))

survdata$Treatment <- as.factor(survdata$Treatment)
```


```{r}
survdata[1, 2] <- survpercsum[4, 4] / (survpercsum[4, 4] + survpercsum[3, 4])
survdata[2, 2] <- survpercsum[12, 4] / (survpercsum[12, 4] + survpercsum[11, 4])
survdata[3, 2] <- survpercsum[20, 4] / (survpercsum[20, 4] + survpercsum[19, 4])
survdata[4, 2] <- survpercsum[28, 4] / (survpercsum[28, 4] + survpercsum[27, 4])
survdata[5, 2] <- survpercsum[36, 4] / (survpercsum[36, 4] + survpercsum[35, 4])



survdata[6, 2] <- survpercsum[6, 4] / (survpercsum[6, 4] + survpercsum[5, 4])
survdata[7, 2] <- survpercsum[14, 4] / (survpercsum[14, 4] + survpercsum[13, 4])
survdata[8, 2] <- survpercsum[22, 4] / (survpercsum[22, 4] + survpercsum[21, 4])
survdata[9, 2] <- survpercsum[30, 4] / (survpercsum[30, 4] + survpercsum[29, 4])
survdata[10, 2] <- survpercsum[38, 4] / (survpercsum[38, 4] + survpercsum[37, 4])


survdata[11, 2] <- survpercsum[8, 4] / (survpercsum[8, 4] + survpercsum[7, 4])
survdata[12, 2] <- survpercsum[16, 4] / (survpercsum[16, 4] + survpercsum[15, 4])
survdata[13, 2] <- survpercsum[24, 4] / (survpercsum[24, 4] + survpercsum[23, 4])
survdata[14, 2] <- survpercsum[32, 4] / (survpercsum[32, 4] + survpercsum[31, 4])
survdata[15, 2] <- survpercsum[40, 4] / (survpercsum[40, 4] + survpercsum[39, 4])

survdata[16, 2] <- survpercsum[2, 4] / (survpercsum[2, 4] + survpercsum[1, 4])
survdata[17, 2] <- survpercsum[10, 4] / (survpercsum[10, 4] + survpercsum[9, 4])
survdata[18, 2] <- survpercsum[18, 4] / (survpercsum[18, 4] + survpercsum[17, 4])
survdata[19, 2] <- survpercsum[26, 4] / (survpercsum[26, 4] + survpercsum[25, 4])
survdata[20, 2] <- survpercsum[34, 4] / (survpercsum[34, 4] + survpercsum[33, 4])
```




```{r}
NCWACAsurv <- ggplot(data = survdata, aes(x = Treatment, y = surv.perc, group = Expt, linetype = Expt, 
                                       shape = Expt)) + 
  theme_bw() + 
  geom_point(size = 3) + 
  geom_line() +
  labs(x = "Temperature Treatment", y = "Proportion surviving to pupation", group = "Experiment", linetype = "Experiment", 
       shape = "Experiment") 
  #scale_linetype_manual(values = c("solid", "dashed", "dotted", "longdashed")) + 
  #scale_shape_manual(values = c(19, 2, 5, 1))

NCWACAsurv
  
```



```{r}
ggsave("~/Desktop/GitHub/Pieris/NCWACAsurv.png", NCWACAsurv, width = 8, height = 5)
```

## 3A. Surv to Pupation vs Temp (by population instead of blocked)
  - Include LPIs
  

```{r}
survpercsum <- summarySE(data = comb, 
                         measurevar = "CID", 
                         groupvars = c("Treatment", "Population", "Surv.pupa"))

survpercsum
```


```{r}
survdata <- data.frame(Treatment = rep(c(16, 21, 26, 30, 34), times = 3), 
                       surv.perc = 0, 
                       Population = rep(c("NC", "WA", "CA"), each = 5))

survdata$Treatment <- as.factor(survdata$Treatment)
```


```{r}
survdata[1, 2] <- survpercsum[4, 4] / (survpercsum[4, 4] + survpercsum[3, 4])
survdata[2, 2] <- survpercsum[10, 4] / (survpercsum[10, 4] + survpercsum[9, 4])
survdata[3, 2] <- survpercsum[16, 4] / (survpercsum[16, 4] + survpercsum[15, 4])
survdata[4, 2] <- survpercsum[22, 4] / (survpercsum[22, 4] + survpercsum[21, 4])
survdata[5, 2] <- survpercsum[28, 4] / (survpercsum[28, 4] + survpercsum[27, 4])



survdata[6, 2] <- survpercsum[6, 4] / (survpercsum[6, 4] + survpercsum[5, 4])
survdata[7, 2] <- survpercsum[12, 4] / (survpercsum[12, 4] + survpercsum[11, 4])
survdata[8, 2] <- survpercsum[18, 4] / (survpercsum[18, 4] + survpercsum[17, 4])
survdata[9, 2] <- survpercsum[24, 4] / (survpercsum[24, 4] + survpercsum[23, 4])
survdata[10, 2] <- survpercsum[30, 4] / (survpercsum[30, 4] + survpercsum[29, 4])

survdata[11, 2] <- survpercsum[2, 4] / (survpercsum[2, 4] + survpercsum[1, 4])
survdata[12, 2] <- survpercsum[8, 4] / (survpercsum[8, 4] + survpercsum[7, 4])
survdata[13, 2] <- survpercsum[14, 4] / (survpercsum[14, 4] + survpercsum[13, 4])
survdata[14, 2] <- survpercsum[20, 4] / (survpercsum[20, 4] + survpercsum[19, 4])
survdata[15, 2] <- survpercsum[26, 4] / (survpercsum[26, 4] + survpercsum[25, 4])


```




```{r}
NCWACAsurv <- ggplot(data = survdata, aes(x = Treatment, y = surv.perc, group = Population, linetype = Population, 
                                       shape = Population)) + 
  theme_bw() + 
  geom_point(size = 3) + 
  geom_line() +
  labs(x = "Mean Rearing Temperature", y = "Proportion surviving to pupation", group = "Population", linetype = "Population", 
       shape = "Population") +
  scale_linetype_manual(values = c("solid", "dashed", "dotted")) + 
  scale_shape_manual(values = c(19, 2, 5))

NCWACAsurv
  
```



```{r}
ggsave("~/Desktop/GitHub/Pieris/NCWACAsurv.png", NCWACAsurv, width = 8, height = 5)
```


#4.North Carolina Experiment Comparisons

```{r}
NCComb <- comb[comb$Population == "NC", ]
```

```{r}
NCdevratemeans <- summarySE(data = NCComb[NCComb$Surv.pupa == "Y", ], 
                               measurevar = "Dev.rate", 
                               groupvars = c("Treatment"))

NCdevratemeans

NCdevratemeans$Treatment <- as.factor(NCdevratemeans$Treatment)
```

```{r}
NCdevrate <- ggplot(data = NCdevratemeans, aes(x = Treatment, y = Dev.rate)) + 
  theme_bw() + 
  geom_point(size = 3) + 
  geom_line(group= 1) +
  labs(x = "Mean Rearing Temperature", y = "Development Rate")

NCdevrate
  
```

```{r}
ggsave("~/Desktop/GitHub/Pieris/NCDevRateComb.png", NCdevrate, width = 8, height = 5)
```

#5. Statistical Analyses

```{r}
popcomb <- lm(Dev.rate ~ Treatment*Population, data = comb)

summary(popcomb)
anova(popcomb)
```
```{r}
comb$Expt = as.factor(comb$Expt)
ncblock <- lm(Dev.rate ~ Treatment*Expt, data = comb[comb$Population == "NC", ])

summary(ncblock)
anova(ncblock)
```

```{r}
nc2sib <- lm(Time.pupa ~ Mean.temp*Sib, data = NC2[is.na(NC2$Time.pupa) == FALSE, ])

summary(nc2sib)
anova(nc2sib)
```

```{r}
nc2hatchloc <- lm(Time.pupa ~ Mean.temp*Hatch.loc, data = NC2[is.na(NC2$Time.pupa) == FALSE, ])

summary(nc2hatchloc)
anova(nc2hatchloc)
```



