---
title: "Pieris_Egg_Gradient"
output: html_document
date: "2023-08-17"
---
 
 Outline:
 0. Packages and data (north carolina and california)
 1. Analyze temperatures- is there significant differences between days or is the temperature of the column consistent?
 2. 
 
 
 
# 0. Packages and data
```{r}
TempData <- read.csv("~/Desktop/GitHub/Pieris/Egg_Gradient/Daily_temps_cleaned.csv", header = TRUE)
```
 
```{r}
library(lmerTest)
```

#1. Analyze temperatures 

## Checking warm temperature gradient first
```{r}
warmgrad <- lm(Temperature ~ Column*Date, data = TempData[TempData$Gradient_type == "warm", ])

anova(warmgrad)

summary(warmgrad)
```

## without the interaction term

```{r}
warmgrad <- lm(Temperature ~ Column+Date, data = TempData[TempData$Gradient_type == "warm", ])

anova(warmgrad)

summary(warmgrad)
```

Okay so date is not a signicant indicator of temperature in the warm temperature gradient (I think)

## Now checking the cooler temperature gradient

```{r}
coolgrad <- lm(Temperature ~ Column*Date, data = TempData[TempData$Gradient_type == "cool", ])

anova(coolgrad)

summary(coolgrad)
```

There might be something going on on June 22nd... 

## Without the interaction term

```{r}
coolgrad <- lm(Temperature ~ Column+Date, data = TempData[TempData$Gradient_type == "cool", ])

anova(coolgrad)

summary(coolgrad)
```

Might need to take a closer look at the 20th and 23rd unless I'm mistaken










