---
title: "Round1_Analysis"
output: html_notebook
---

0. Load in packages and data sets
1. Compare mass and dev time of larval pupal intermediates with pupae across temps
2. Compare mass and dev time of deformed adults with adults across temps
3. Make data frame with means and standard errors across temps
4. Make graphs 

# 0. Load in packages and data sets
```{r}
library(dplyr)
library(ggplot2)
library(lmerTest)
```
```{r}
data <- read.csv("~/Desktop/Github/Pieris/Data/CleanedRound1.csv", header = TRUE)

data$Mean.Temp <- as.factor(data$Mean.Temp)
```

# 1. Compare larval pupal ints with successful pupae

## Mass at pupation

```{r}
masspupae <- lm(Mass.pupa ~ PupateOk*Mean.Temp, data = data[data$Surv.pupa == "Y", ])

anova(masspupae)

summary(masspupae)
```
Drop the non-significant interaction term


```{r}
masspupaeadd <- lm(Mass.pupa ~ PupateOk + Mean.Temp, data = data[data$Surv.pupa == "Y", ])

anova(masspupaeadd)

summary(masspupaeadd)
```


## Time at pupation


```{r}
timepupae <- lm(Time.pupa ~ PupateOk*Mean.Temp, data = data[data$Surv.pupa == "Y", ])

anova(timepupae)

summary(timepupae)
```

Drop insignificant interaction term

```{r}
timepupaeadd <- lm(Time.pupa ~ PupateOk + Mean.Temp, data = data[data$Surv.pupa == "Y", ])

anova(timepupaeadd)

summary(timepupaeadd)
```

