---
title: "WA_Analysis"
output: html_notebook
---

This script will graph and analyze all of the Washington data. 

0. Load in data and packages
1. Manipulate data
2. Graph
  a. Dev rate vs. dev temp - hatch to pupa
  b. Dev rate vs. dev temp - pupa to eclos
  c. Survival vs. dev temp - hatch to pupa
  d. Survival vs. dev temp - pupa to eclos (just pupa data)
  e. Survival vs. dev temp - pupa to eclos (block 1+2 data)
3. Subsequent analyses as needed

# 0. Load in data 

```{r}
library(tidyverse)
library(Rmisc)
```

```{r}
block1 <- read.csv("~/Desktop/GitHub/Pieris/Washington/DataWA/CleanedBlock1.csv", header = TRUE)
block2 <- read.csv("~/Desktop/GitHub/Pieris/Washington/DataWA/CleanedBlock2.csv", header = TRUE)
pupa <- read.csv("~/Desktop/GitHub/Pieris/Washington/DataWA/CleanedPupa.csv", header = TRUE)
```

# 1. Manipulate data

Change temp to factor

```{r}
block1$Treatment <- as.factor(block1$Treatment)
block2$Treatment <- as.factor(block2$Treatment)
pupa$Trt <- as.factor(pupa$Trt)
```

Add block designation to datasets and combine

```{r}
block1$Block <- 1
block2$Block <- 2
```

```{r}
blockcomb <- rbind(block1, block2)
```


# 2. Graph

## a. dev rate vs dev temp (H-P)

Get dev rate (1/dev time)

```{r}
blockcomb$Dev.Rate.P <- 1/(blockcomb$DaysHtoP)
```

Summarize the data 

```{r}
devratepmeans <- summarySE(data = blockcomb[blockcomb$Surv.pupa == "Y", ], measurevar = "Dev.Rate.P", 
                           groupvars = c("Treatment", "PupateOK"))

devratepmeans
```

  Graph! 
  
```{r}
devratepgraph <- ggplot(data = devratepmeans, aes(x = Treatment, y = Dev.Rate.P, group = PupateOK, shape = PupateOK)) + 
  theme_bw() + 
  geom_point(size = 3) + 
  geom_errorbar(aes(ymin = Dev.Rate.P - se, ymax = Dev.Rate.P + se), width = 0.3) + 
  scale_shape_manual(values = c(21, 19)) + 
  geom_line(aes(linetype = PupateOK)) + 
  scale_linetype_manual(values = c("dotdash", "solid")) + 
  labs(x = "Temperature Treatment", y = "Development Rate", shape = "Successful Pupation", linetype = "Successful Pupation")

devratepgraph
```
  
## b. dev rate vs dev temp (p-e)
  
Get dev rate (1/dev time)

```{r}
blockcomb$Dev.Rate.E <- 1/(blockcomb$DaysPtoE)
```

Summarize the data 

```{r}
devrateemeans <- summarySE(data = blockcomb[blockcomb$Surv.eclos == "Y", ], measurevar = "Dev.Rate.E", 
                           groupvars = c("Treatment"))

devrateemeans
```


graph!

```{r}
devrateegraph <- ggplot(data = devrateemeans, aes(x = Treatment, y = Dev.Rate.E)) + 
  theme_bw() + 
  geom_point(size = 3) + 
  geom_errorbar(aes(ymin = Dev.Rate.E - se, ymax = Dev.Rate.E + se), width = 0.3) + 
  scale_shape_manual(values = c(21, 19)) + 
  geom_line() + 
  scale_linetype_manual(values = c("solid")) + 
  labs(x = "Temperature Treatment", y = "Development Rate")

devrateegraph
```

## 3.  Survival vs dev temp

dev temp on x axis, survival on right axis (amt survived to each respective stage)


```

## Survival to pupation vs temp treatment 

1. Create summary table
2. Create blank table for input
3. Hard code input
4. Graph it

### 1. Create summary table

```{r}
survpercsum <- summarySE(data = data, 
                         measurevar = "Mass.pupa", 
                         groupvars = c("Mean.Temp", "Surv.pupa"))
```

### 2. Create blank table

```{r}
survdata <- data.frame(Mean.Temp = c(16, 21, 26, 30, 34), 
                       surv.perc = 0, 
                       group = 1)

survdata$Mean.Temp <- as.factor(survdata$Mean.Temp)
survdata$group = as.factor(survdata$group)
```

### 3. Hard code it

```{r}
survdata[1, 2] <- survpercsum[2, 3] / (survpercsum[2, 3] + survpercsum[1, 3])
survdata[2, 2] <- survpercsum[4, 3] / (survpercsum[4, 3] + survpercsum[3, 3])
survdata[3, 2] <- survpercsum[6, 3] / (survpercsum[6, 3] + survpercsum[5, 3])
survdata[4, 2] <- survpercsum[8, 3] / (survpercsum[8, 3] + survpercsum[7, 3])
survdata[5, 2] <- survpercsum[10, 3] / (survpercsum[10, 3] + survpercsum[9, 3])
```

### 4. Graph it

```{r}
survgraph <- ggplot(data = survdata, aes(x = Mean.Temp, y = surv.perc, group = group)) + 
  theme_bw() + 
  geom_point(size = 2) + 
  geom_line() + 
  ylim(0, 1) + 
  labs(x = "Temperature treatment", y = "Proportion survival to pupation")

survgraph
```

```{r}
ggsave("~/Desktop/GitHub/Pieris/Figures/survgraph.png", survgraph, width = 8, height = 5)
```
