---
title: "WA_Cleaning "
output: html_notebook
---

This notebook is going to clean all 3 datasets from the WA studies Dec22-Jan23, one dataset at a time. 

0. Load in packages and data sets 
1. Add in survival binaries (pupation, eclosion)
2. Add in larval-pupal int binary 
3. Save the output files 

# 0. Load in packages and datasets

```{r}
library(dplyr)
```

```{r}
block1 <- read.csv("~/Desktop/GitHub/Pieris/Washington/DataWA/WABlock1Dev.csv", header = TRUE)
block2 <- read.csv("~/Desktop/GitHub/Pieris/Washington/DataWA/WABlock2Dev.csv", header = TRUE)
pupa <- read.csv("~/Desktop/GitHub/Pieris/Washington/DataWA/WAPupa.csv", header = TRUE)
```

# 1. Block 1 first 

## Make for loops 

Larval-pupal intermediates

```{r}
block1$PupateOK <- NA
```

```{r}
for (i in 1:length(block1$PupateOK)){
  if(is.na(block1[i, 17]) == FALSE){
    block1[i, 26] <- "N"
  } else if(is.na(block1[i, 17]) == TRUE && is.na(block1[i, 15]) == FALSE){
    block1[i, 26] <- "Y"
  } else if(is.na(block1[i, 17]) == TRUE && is.na(block1[i, 15]) == TRUE){
    block1[i, 26] <- NA
  }
}
```

Survival to pupation

```{r}
block1$Surv.pupa <- "N"
```

```{r}
for (i in 1:length(block1$Surv.pupa)){
  if(is.na(block1[i, 17]) == FALSE | is.na(block1[i, 15]) == FALSE){
    block1[i, 27] <- "Y"
  } else if (is.na(block1[i, 17]) == TRUE & is.na(block1[i, 15]) == TRUE){
    block1[i, 27] <- "N"
  }
}
```

Survival to eclosion

```{r}
block1$Surv.eclos <- "N"
```

```{r}
for (i in 1:length(block1$Surv.eclos)) {
  if(is.na(block1[i, 24]) == FALSE) {
    block1[i, 28] <- "Y"
  } else if (is.na(block1[i, 24]) == TRUE) {
    block1[i, 28] <- "N"
  }
}
```

## Save as output file 

Clean up data files 

```{r}
block1clean <- block1 %>%
  select(CID, Treatment, Mass.pupa, Mass.larvapupa.int, DaysHtoP, DaysPtoE, PupateOK, Surv.pupa, Surv.eclos)
```

```{r}
write.csv(block1clean, file = "~/Desktop/GitHub/Pieris/Washington/DataWA/CleanedBlock1.csv")
```

# 2. Block 2

## Write for loops 

Larval-pupal intermediates


```{r}
block2$PupateOK <- NA
```

```{r}
for (i in 1:length(block2$PupateOK)) {
  if(is.na(block2[i, 16]) == FALSE){
    block2[i, 25] <- "N"
  } else if(is.na(block2[1, 16]) == TRUE && is.na(block2[i, 14]) == FALSE){
    block2[i, 25] <- "Y"
  } else if(is.na(block2[1, 16]) == TRUE && is.na(block2[i, 14]) == TRUE){
    block2[i, 25] <- NA
  }
}
```


Survival to pupation

```{r}
block2$Surv.pupa <- "N"
```


```{r}
for (i in 1:length(block2$Surv.pupa)){
  if(is.na(block2[i, 16]) == FALSE | is.na(block2[i, 14]) == FALSE){
    block2[i, 26] <- "Y"
  } else if (is.na(block2[i, 16]) == TRUE & is.na(block2[i, 14]) == TRUE){
    block2[i, 26] <- "N"
  }
}
```



Survival to eclosion

```{r}
block2$Surv.eclos <- "N"
```

```{r}
for (i in 1:length(block2$Surv.eclos)){
  if(is.na(block2[i, 23]) == FALSE){
    block2[i, 27] <- "Y"
  } else if (is.na(block2[i, 23]) == TRUE){
    block2[i, 27] <- "N"
  }
}
```


## Write output file

Clean up data files 

```{r}
block2clean <- block2 %>%
  select(CID, Treatment, Mass.pupa, Mass.larvapupa.int, DaysHtoP, DaysPtoE, PupateOK, Surv.pupa, Surv.eclos)
```

```{r}
write.csv(block2clean, file = "~/Desktop/GitHub/Pieris/Washington/DataWA/CleanedBlock2.csv")
```


# 3. Pupal data

## Write for loops

Larval pupal intermediates


```{r}
pupa$PupateOK <- NA
```

```{r}
for (i in 1:length(pupa$PupateOK)){
  if(is.na(pupa[i, 12]) == FALSE){
    pupa[i, 21] <- "N"
  } else if(is.na(pupa[i, 12]) == TRUE && is.na(pupa[i, 10]) == FALSE){
    pupa[i, 21] <- "Y"
  } else if(is.na(pupa[i, 12]) == TRUE && is.na(pupa[i, 10]) == TRUE){
    pupa[i, 21] <- NA
  }
}
```

Survival to eclosion


```{r}
pupa$Surv.eclos <- "N"
```

```{r}
for (i in 1:length(pupa$Surv.eclos)){
  if(is.na(pupa[i, 19]) == FALSE){
    pupa[i, 22] <- "Y"
  } else if(is.na(pupa[i, 19]) == TRUE){
    pupa[i, 22] <- "N"
  }
}
```


## Write output file 

Clean up data files 

```{r}
pupaclean <- pupa %>%
  select(MRID, Trt, Mass.Pupa, Mass.INT, DaysHtoP, DaysPtoE, PupateOK, Surv.eclos)
```

```{r}
write.csv(pupaclean, file = "~/Desktop/GitHub/Pieris/Washington/DataWA/CleanedPupa.csv")
```
